### 2019-01-08 paper/sex_selection_spacing-ver2.tex
Reorder packages to run and minor edits in recall section

\usepackage{fontspec}
\setromanfont[Ligatures=TeX]{TeX Gyre Pagella}
\usepackage{unicode-math}
\setmathfont{TeX Gyre Pagella Math}
\usepackage{amsmath}
\usepackage[title]{appendix}
\usepackage[margin=1.0in]{geometry}
\usepackage[figuresleft]{rotating}
\usepackage[longnamesfirst]{natbib}
\usepackage{dcolumn}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{setspace}
\usepackage[justification=centering]{caption}
\usepackage[font=scriptsize]{subfig}
\usepackage[xetex,colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
\usepackage{adjustbox}
\usepackage{xfrac}

@@

The relationship between length of marriage and recall error can also seen in 
Figure \ref{fig:sexRatioMarriage}, which shows the observed sex ratio for children reported
as first born as a function of duration of marriage at the time of the survey combining 
all four surveys.
The solid line is the sex ratio of children reported 
as first born by the number of years between the survey and marriage, 
the dashed lines indicate the 95 percent confidence interval 
and the horizontal line the natural sex ratio (approximately 0.512).
To ensure sufficient cell sizes the years are grouped in twos.
In line with the results from Tables \ref{tab:recallMarriageBO1} and 
\ref{tab:recallMarriageBO2}, the observed ratio of boys 
is increasingly above the expected value the longer ago the parents were married.%
\footnote{
The graph for second births shows a similar pattern with the
likelihood of the second child being a boy going up with increasing marriage duration.
The graphs for the second births and the individual survey rounds are available upon request.
}

\begin{figure}[htp]%
\centering
\includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
\caption{Sex ratio of ``first'' births by duration of marriage}
\label{fig:sexRatioMarriage}}
\end{figure}

@@

% \begin{figure}
% \centering
% \subfloat[NFHS-1]{\includegraphics[width=.49\textwidth]{des_b1_m_age_r1}}
% \subfloat[NFHS-2]{\includegraphics[width=.49\textwidth]{des_b1_m_age_r2}} \\
% \subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{des_b1_m_age_r3}} 
% \caption{Ratio of Boys for ``First'' Births by Survey Round}
% \label{fig:sex_ratio_recall_rounds}
% \end{figure}

>>>>

\usepackage{amsmath}
\usepackage{fontspec}
\setromanfont[Ligatures=TeX]{TeX Gyre Pagella}
\usepackage{unicode-math}
\setmathfont{TeX Gyre Pagella Math}
\usepackage[title]{appendix}
\usepackage[margin=1.0in]{geometry}
\usepackage[figuresleft]{rotating}
\usepackage[longnamesfirst]{natbib}
\usepackage{dcolumn}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{setspace}
\usepackage[justification=centering]{caption}
\usepackage[font=scriptsize]{subfig}
\usepackage[xetex,colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black]{hyperref}
\usepackage{adjustbox}
\usepackage{xfrac}

@@

The relationship between length of marriage and recall error can also seen in 
Figure \ref{fig:sexRatioMarriage}, which shows the observed sex ratio for children reported
as first born as a function of duration of marriage at the time of the survey combining 
all four surveys.
The solid line is the sex ratio of children reported 
as first born by the number of years between the survey and marriage, 
the dashed lines indicate the 95 percent confidence interval 
and the horizontal line the natural sex ratio (approximately 0.512).
To ensure sufficient cell sizes the years are grouped in twos.
In line with the results from Tables \ref{tab:recallMarriageBO1} and 
\ref{tab:recallMarriageBO2}, the observed ratio of boys 
is increasingly above the expected value the longer ago the parents were married.

\begin{figure}[htp]%
\centering
\includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
\caption{Sex ratio of ``first'' births by duration of marriage}
\label{fig:sexRatioMarriage}
\end{figure}

@@

\begin{figure}
\centering
\subfloat[NFHS-1]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_1}}
\subfloat[NFHS-2]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_2}} \\
\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_3}} 
\subfloat[NFHS-3]{\includegraphics[width=.49\textwidth]{recall_sex_ratio_marriage_round_4}} 
\caption{Ratio of Boys for ``First'' Births by Survey Round}
\label{fig:sex_ratio_recall_rounds}
\end{figure}
